---
title: "Example 4"
author: "Sabina Rosca"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("~/wur_bfast_workshop/R-scripts/tutorial_0.R")
source("~/wur_bfast_workshop/R-scripts/accuracy_assessment.R")
```

## Example 4

Vegetation index: NDMI

History period: 2005-2010

option: "all"

stack subset: yes (from 2005)

Monitoring approach: 2010-2016

option: Full monitoring period approach

Regression model: harmonic order 1

Trend: no

```{r, eval=FALSE}
source("~/wur_bfast_workshop/R-scripts/tutorial_0.R")
source("~/wur_bfast_workshop/R-scripts/accuracy_assessment.R")
example_title <- 4
results_directory <- file.path(results_directory,paste0("example_",example_title))
dir.create(results_directory)
log_filename <- file.path(results_directory, paste0(format(Sys.time(), "%Y-%m-%d-%H-%M-%S"), "_example_", example_title, ".log"))
start_time <- format(Sys.time(), "%Y/%m/%d %H:%M:%S")

result <- file.path(results_directory, paste0("example_", example_title, ".grd"))
subsetTimeStack <- function(timestack,year){
  timespan <- which(timestack@z$time>as.Date(paste0(year,"-01-01"),"%Y-%m-%d"))
  result <- brick(timestack[[timespan]])
  result@z$time <- timestack@z$time[timespan]
  result
}

ndmiStack_example_4 <- subsetTimeStack(ndmiStack,2005)
time <- system.time(bfmSpatial(ndmiStack_example_4, start = c(2010, 1),
                               formula = response ~ harmon,
                               order = 1, history = "all",
                               filename = result,
                               mc.cores = detectCores()))

write(paste0("This process started on ", start_time,
             " and ended on ",format(Sys.time(),"%Y/%m/%d %H:%M:%S"),
             " for a total time of ", time[[3]]/60," minutes"), log_filename, append=TRUE)
```

## Post Processing

```{r,include=FALSE}
example_title <- 4
results_directory <- file.path(results_directory,paste0("example_",example_title))
result <- file.path(results_directory, paste0("example_", example_title, ".grd"))
```

```{r}
bfm_ndmi <- brick(result)
#### Change
change <- raster(bfm_ndmi,1)
plot(change, col=rainbow(7),breaks=c(2010:2016))

#### Magnitude
magnitude <- raster(bfm_ndmi,2)
magn_bkp <- magnitude
magn_bkp[is.na(change)] <- NA
plot(magn_bkp,breaks=c(-5:5*1000),col=rainbow(length(c(-5:5*1000))))
plot(magnitude, breaks=c(-5:5*1000),col=rainbow(length(c(-5:5*1000))))

#### Error
error <- raster(bfm_ndmi,3)
plot(error)

#### Detect deforestation
def_ndmi <- magn_bkp
def_ndmi[def_ndmi>0]=NA
plot(def_ndmi)
plot(def_ndmi,col="black", main="NDMI_deforestation")
writeRaster(def_ndmi,filename = file.path(results_directory,paste0("example_",example_title,"_deforestation_magnitude.grd")),overwrite=TRUE)

def_years <- change
def_years[is.na(def_ndmi)]=NA

years <- c(2010,2011,2012,2013,2014,2015,2016,2017)
plot(def_years, col=rainbow(length(years)),breaks=years, main="Detecting deforestation after 2010")
writeRaster(def_ndmi,filename = file.path(results_directory,paste0("example_",example_title,"_deforestation_dates.grd")),overwrite=TRUE)

```

## Accuracy Asessment

```{r}
Forest_mask <- raster(file.path(workshop_folder,"data/Fmask_2010_Peru.tif"))
validation_forest_map <- raster(file.path(workshop_folder,"data/Validation_forest_2016.tif"))
```

The accuracy assessment is done following the paper of Olofsson et al. (2014) "Good practices for estimating area and assessing accuracy of land change".

```{r warning=FALSE}
sample_size <- calcSampleSize(def_years,Forest_mask,c(0.9,0.7),0.01)
samples <- extractRandomSamples(def_years,Forest_mask,sample_size,results_directory,"samples")
val_sample <- extractValidationValues(validation_forest_map, samples, Forest_mask)
conf_matrix <- assessAcuracy(samples,val_sample)
conf_matrix
```